---
title: "Assignment 1"
author: "Raveena, Alanna, Jack"
date: "10/21/2021"
output: html_document
---

# Research Question
How do food access and demographic characteristics impact mental and physical health on a county scale?

# Prior Research - AlL

# Data

# Load Data
```{r, message = FALSE, results = FALSE}
library(tidyverse)
library(tidycensus)
library(readxl)
library(knitr)
```

## USDA - Food Access Research Database - 2019 - JACK
* Access to food options within 1 mile urban or 10 miles rural
* SNAP recipients by housing units
* Percent of households using SNAP
* Poverty rate
```{r}
USDA <- read_csv("Food Access Research Atlas.csv") %>%
  mutate(CensusTract = case_when(str_length(as.character(CensusTract)) == 11 ~ as.character(CensusTract),
                           str_length(as.character(CensusTract)) == 10 ~ paste("0", CensusTract, sep=""),
                           TRUE ~ "not a tract")) %>%
  mutate(pct_SNAP = TractSNAP / OHU2010) %>%
  filter(CensusTract != "not a tract") %>%
  select(CensusTract, TractSNAP, OHU2010, pct_SNAP, PovertyRate, LA1and10)
```

## Census Data - 2010 - RAVEENA
* Age
* Education
* Median Income
* Household size
* Households with children
* Race
```{r}
```

## CDC - PLACES - 2018 - ALANNA
* Mental Health
* Physical Health
```{r}
```

## CDC - MRFEI - 2011 - RAVEENA
* Healthy Food Sources
```{r}
```

## Combine Data into One Table
```{r}
```

# References
