---
title: "Assignment 1"
author: "Raveena, Alanna, Jack"
date: "10/21/2021"
output: html_document
---

# Research Question
How do food access and demographic characteristics impact mental and physical health on a county scale?

# Prior Research - AlL
Seligman and Schillinger (2010) posit that food insecurity and chronic disease follows a cyclical pattern where food insecurity leads to chronic disease, thereby increasing medical costs and causing low income households to make trade-offs in spending, often leading to less money available to address food insecurity.

# Data

# Load Data
```{r, message = FALSE, results = FALSE}
library(tidyverse)
library(tidycensus)
library(readxl)
library(knitr)
```

## USDA - Food Access Research Database - 2019 - JACK
* Access to food options within 1 mile urban or 10 miles rural
* SNAP recipients by housing units
* Percent of households using SNAP
* Poverty rate
```{r, message = FALSE, results = FALSE, warning = FALSE}
USDA <- read_csv("Food Access Research Atlas.csv") %>%
  mutate(CensusTract = case_when(str_length(as.character(CensusTract)) == 11 ~ as.character(CensusTract),
                           str_length(as.character(CensusTract)) == 10 ~ paste("0", CensusTract, sep=""),
                           TRUE ~ "not a tract")) %>%
  mutate(pct_SNAP = TractSNAP / OHU2010) %>%
  filter(CensusTract != "not a tract") %>%
  rename(GEOID = CensusTract)%>%
  select(GEOID, TractSNAP, OHU2010, pct_SNAP, PovertyRate, LA1and10)
```

## Census Data - 2010 - RAVEENA
* Age
* Education
* Median Income
* Household size
* Households with children
* Race
```{r}

all_states <- c(state.abb)

censusMedAge <- get_decennial(geography = "tract", 
                        year = 2010,
                        variables = c(MedAge = "P013001"),
                        output = "wide",
                        state = all_states,
                        geometry = TRUE)
  
censusHouseSize <- get_decennial(geography = "tract", 
                        year = 2010,
                        variables = c(HSTotal = "H013001",
                                      HSOne = "H013002",
                                      HSTwo = "H013003",
                                      HSThree = "H013004",
                                      HSFour = "H013005",
                                      HSFive = "H013006",
                                      HSSix = "H013007",
                                      HSSevenPlus = "H013008"),
                        output = "wide",
                        state = all_states,
                        geometry = FALSE)

censusChildren <- get_decennial(geography = "tract", 
                        year = 2010,
                        variables = c(OwnWChildren = "H019003",
                                      RentWChildren = "H019006"),
                        output = "wide",
                        state = all_states,
                        geometry = FALSE)

censusRace <- get_decennial(geography = "tract", 
                        year = 2010,
                        variables = c(RTotal = "P010001",
                                      RWhite = "P010002",
                                      RBlack = "P010003",
                                      RAI = "P010004",
                                      RAsian = "P010005",
                                      RNH = "P010006",
                                      ROther = "P010007",
                                      RTwoPlus = "P010008"),
                        output = "wide",
                        state = all_states,
                        geometry = FALSE)

acsEducation<- get_acs(geography = "tract", 
                   variables = c(EdTotal = "B15003_001",
                                 EdHighSchool = "B15003_017",
                                 EdGED = "B15003_018",
                                 EdAssociates = "B15003_021",
                                 EdBachelors = "B15003_022",
                                 EdMasters = "B15003_023",
                                 EdProfessional = "B15003_024",
                                 EdDoctorate = "B15003_025"), 
                   state = all_states,
                   output = "wide",
                   geometry = FALSE)

acsMedIncome<- get_acs(geography = "tract", 
                   variables = c(MedIncome = "B06011_001"), 
                   state = all_states,
                   output = "wide",
                   geometry = FALSE)
```

## CDC - PLACES - 2018 - ALANNA
* Mental Health
* Physical Health
```{r}
```

## CDC - MRFEI - 2011 - RAVEENA
* Healthy Food Sources
```{r}
CDC_MRFEI <- read_excel(path = "2_16_mrfei_data_table.xls", 
                      sheet = "MRFEI According to Census Tract") %>%
  rename(GEOID = fips)%>%
  select(GEOID,mrfei)
```

## Combine Data into One Table
```{r}
```

# References
Centers for Disease Control and Prevention, "Census Tract Level State Maps of the Modified Retail Food Environment Index (mRFEI)" https://www.cdc.gov/obesity/downloads/census-tract-level-state-maps-mrfei_TAG508.pdf

Seligman, Hilary K., and Dean Schillinger. "Hunger and Socioeconomic Disparities in Chronic Disease." The New England Journal of Medicine 363, no. 1 (2010): 6-9.

United States Census Bureau. American Community Survey, 5-year estimates. 2019.

United States Census Bureau. 2010.

United States Department of Agriculture. "Food Access Research Atlas". 2019. "https://www.ers.usda.gov/data-products/food-access-research-atlas/download-the-data/"